---
title: "TinyML"
author: "Asif Anwar"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## TinyML Project

To find the statistical significant difference between the performance of the two models, we can use conduct an experiment with paired t-test from numerical outcomes from each model from same samples. Here the interest is a possible difference between the to outcomes. 

## Paired t-test 
As per the the paired t-test method, we test the null hypothesis H_0: mu=0 that the mean of this population is 0. The analysis is simply a one sample analysis on the difference of the means of x-population and y-population. 

```{r}
outcome = read.csv(file = "results_1000_v2.csv" )
outcome
```


```{r, fig.asp=0.35}
par(mfrow=c(1,3))
plot(full~tflite_int, pch=actual, col=actual, data=outcome)
abline(0,1)
boxplot(outcome$full, outcome$tflite_int)
boxplot(outcome$full~outcome$tflite_int)

```

```{r}
t.test(outcome$full, outcome$tflite_int, paired=T)
```

H_0 is rejected, mean of the difference is different from 0 

```{r}
t.test(outcome$full ~ outcome$tflite_int)
```


```{r}
qqnorm(c(outcome$model)~c(outcome$tfmodel))
```

```{r}
shapiro.test(outcome$model ~ outcome$tfmodel)
```


```{r}
x = outcome$model
x = as.numeric(x)
is.numeric(x)

y = outcome$tfmodel
y = as.numeric(y)
is.numeric(y)
```


```{r}
is.numeric(x)
shapiro.test(x~y)
```

```{r, fig.asp=0.33}
#attach(peruvians)
par(mfrow=c(1,3))
plot(x,y)
```

```{r, fig.align='center', fig.asp=0.55}
par(mfrow=c(1,2))
qqnorm(x)
qqnorm(y)
```


```{r}
ks.test(outcome$full, outcome$tflite_int)
```


```{r}
diff = table(outcome$full -outcome$tflite_int)
diff
```

```{r}

```

